Methodology for Assessing the State of the Practice for Domain X

### 2020-03-12 StateOfPractice/Methodology/Methodology.tex
Updates to Methodology for assessing quality

@@

\section{Quality Measures}

Go through each quality and describe how it will be measured.

Start with decided upon definition.  (If discussion is on-going, please select
the ``best'' definition, but include a warning that it may change.)

>>>>

\section{Overview of Steps in Assessing Quality of the Domain Software}

\begin{enumerate}
\item Identify domain.  (Provide criteria on a candidate domain.)
\item 
\end{enumerate}

\section{Identify Candidate Software}

@@

\section{Empirical Measures}

Measures that can be extracted from on-line repos.

\section{User Experiments}

Describe experiments with users to assess usability, performance etc.

\section{Analytic Hierarchy Process}

Describe process.  Domain expert review.

\section{Quality Specific Measures}
